Model_CFU

### 2017-01-23 code/HumanCdGF_cdiff_colonization.Rmd

```{r NMDS of Colonization Level, eval=F}
setwd('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/')
full_shared_file <- 'data/process/full_shared.shared'
full_shared_file <- read.table(full_shared_file, sep = '\t', header = T)

@@

nmds <- metaMDS(dist_matrix)
stressplot(nmds)
plot(nmds, type = 'n')

#points(nmds, display = 'sites', pch = 21, bg = as.numeric(as.factor(nmds_df$human_source)))
#text(nmds, display = 'species', cex = 0.5)
#envfit(nmds ~ )
```

>>>>

```{r NMDS of Colonization Level, fig.height=6, fig.width=6}
setwd('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/')
full_shared_file <- 'data/process/full_shared.shared'
full_shared_file <- read.table(full_shared_file, sep = '\t', header = T)

@@

nmds_group <- colonized_cfu %>% 
    select(mouse_id, human_source, log_cfu_med) %>% 
    right_join(community_all_d0) %>% 
    filter(!is.na(log_cfu_med)) %>% 
    mutate(colonization_level= ifelse(log_cfu_med >= 8.25, 'hi',
                                     ifelse(log_cfu_med <= 6.5, 'lo', 'mid'))) %>% 
    select(colonization_level, mouse_id)

rownames(dist_matrix) <- gsub('_D0','',rownames(dist_matrix))
colnames(dist_matrix) <- gsub('_D0','',colnames(dist_matrix))

nmds <- metaMDS(dist_matrix)
#stressplot(nmds)
colors <- c('red','green','orange')

plot(nmds, type = 'n')
points(nmds, display = 'sites', pch = 21, bg = colors[as.numeric(factor(nmds_group$colonization_level))])
legend('topright', c('High (> 8.25 Log10 CFU)','Middle (8.25-6.5 Log10 CFU)','Low (< 6.5 Log10 CFU)'), 
       pch =21, pt.bg=c('red','orange','green'), inset=0.09, box.lty = 0)
#adonis(dist_matrix~colonization_level, data = nmds_group)
```

Stress = `r nmds$stress`

##### AMOVA
hi-lo-mid	Among	  Within	Total
SS	      4.48543	8.08716	12.5726
df	      2	      30	    32
MS	      2.24272	0.269572

Fs:	7.68145
p-value: <0.001*
###### significantly different centroids

#### HOMOVA
HOMOVA	  BValue  	P-value	  SSwithin/(Ni-1)_values
hi-lo-mid	21.6225	  <0.001*	  0.000145266	0.0966271	0.370517
hi-lo	    14.1638	  <0.001*	  0.000145266	0.0966271
hi-mid	  18.2515 	<0.001*	  0.000145266	0.370517
lo-mid	  3.48295 	<0.001*	  0.0966271	0.370517
